Tropical Andes plant Lookup Table

### 2023-11-08 code/L1/L1_P2_TropicalAndes_taxcleaning.Rmd
combine harmonization results to create lookup table, apply lookup table to GBIF data

# Use Rocc to check scientific names 
Adapted from tutorial https://liibre.github.io/Rocc/articles/articles/check_taxa.html
```{r}
name_check_results <- bdc_clean_names(sci_names = all_species, save_outputs = FALSE)
```
```{r}
all_species_cleaned <- name_check_results$names_clean
```

@@

@@

@@

```{r}
# combine to create lookup table
lookup_table <- rbind(species_matches, species_corrected)
```

# Save lookup table as csv
```{r}

# Update data files species names using lookup table
```{r}

>>>>

# Use bdc to check scientific names 
```{r}
name_check_results <- bdc_clean_names(sci_names = all_species, save_outputs = FALSE)
```
```{r}
all_species_cleaned <- name_check_results$names_clean
```

@@

# Create list of species still unharmonized
```{r}
unresolved_species <- all_species_col_NA$original_search
```

@@

```{r}
#combine
lookup_table_TNRS <- rbind(species_matches, species_corrected)
lookup_table_TNRS$harmonization_package <- c("TNRS")
```

@@

```{r}
#update col names
colnames(species_col_accepted) <- c("Name_submitted", "Name_matched", "Source")
colnames(species_col_synonmyn) <- c("Name_submitted", "Name_matched", "Source")
```

```{r}
#combine
lookup_table_bdc <- rbind(species_col_accepted, species_col_synonmyn)
lookup_table_bdc$harmonization_package <- c("bdc")
```

## Combine to create lookup table
```{r}
lookup_table <- rbind(lookup_table_TNRS, lookup_table_bdc)
nrow(lookup_table)
```

# Save lookup table as csv
```{r}
write.csv(lookup_table, file.path(output_path,"plant_lookup_table.csv"))
```

# Update data files species names using lookup table
## GBIF
```{r}
# filter data to species in lookup_table$Names_submitted
GBIF_occ_subset <- GBIF_occ %>%
  filter(species %in% lookup_table$Name_submitted)
nrow(GBIF_occ_subset)
# replace species with lookup_table$Name_matched
GBIF_occ_subset_harmonized <- GBIF_occ_subset %>% mutate(species = replace(species, species %in% lookup_table$Name_submitted, lookup_table$Name_matched))
nrow(GBIF_occ_subset_harmonized)
```

# Summary
```{r}
